Limitations on the Two-Infall Scenario in the Era of Large Stellar Age Catalogs

### 2025-04-29 src/tex/ms.tex

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/ofe_feh_best.pdf}
    \caption{Stellar abundance distributions across the disk predicted by our best multi-zone model, with \yZ{2}, ${\rm [X/H]}_{\rm CGM}=-0.7$, $f_\Sigma(R_\odot)=0.25$, and $\eta_\odot=1.8$. Each panel presents a random mass-weighted sample of \num{10000} stellar populations that are drawn from the given ($R_{\rm gal}$, $|z|$) bin and color-coded by age. A Gaussian scatter is applied to each point according to the median age ($\tau_{\rm NN}$) and abundance uncertainties in Table \ref{tab:uncertainties}. The solid and dashed contours enclose 30\% and 80\%, respectively, of the APOGEE data in each region. {\bf Key takeaway:} The predicted distribution from the two-infall model lines up with the APOGEE distribution close to the midplane, but agreement is worse at higher latitudes and in the outer Galaxy.}
    \label{fig:ofe-feh-best}
\end{figure*}

>>>>

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/ofe_feh_best.pdf}
    \caption{Stellar abundance distributions across the disk predicted by our best multi-zone model, with \yZ{2}, ${\rm [X/H]}_{\rm CGM}=-0.7$, $f_\Sigma(R_\odot)=0.25$, $\sigma_{\rm RM8}=3.6\kpc$, and $\eta_\odot=1.8$. Each panel presents a random mass-weighted sample of \num{10000} stellar populations that are drawn from the given ($R_{\rm gal}$, $|z|$) bin and color-coded by age. A Gaussian scatter is applied to each point according to the median age ($\tau_{\rm NN}$) and abundance uncertainties in Table \ref{tab:uncertainties}. The solid and dashed contours enclose 30\% and 80\%, respectively, of the APOGEE data in each region. {\bf Key takeaway:} The predicted distribution from the two-infall model lines up with the APOGEE distribution close to the midplane, but agreement is worse at higher latitudes and in the outer Galaxy.}
    \label{fig:ofe-feh-best}
\end{figure*}

Motivated by the results of the previous sections, we construct a model which attempts to solve all of the issues that have been outlined thus far. Our ``best attempt'' model uses the \yZ{2} yield set to flatten the local age--metallicity relation (Figure \ref{fig:abundance-evolution-yields}), pre-enriched infall at the level of $\mathXH_{\rm CGM}=-0.7$ to reduce the dilution at $t_{\rm max}$ (Figure \ref{fig:abundance-evolution-params}), slightly stronger outflows with $\eta_\odot=1.8$ to maintain the local equilibrium at Solar metallicity, moderately stronger radial migration with $\sigma_{\rm RM8}=3.6\kpc$ to widen the local metallicity dispersion (Figure \ref{fig:abundance-evolution-params}), and a greater local disk ratio $f_\Sigma(R_\odot)=0.25$ to reduce the width of the low-$\alpha$ distribution and beef up the high-$\alpha$ sequence (Figure \ref{fig:ofe-distribution-parameters}). Our choices for $\mathXH_{\rm CGM}$, $\sigma_{\rm RM8}$, and $f_\Sigma(R_\odot)$ are more moderate, and we believe more realistic, than in previous sections to avoid extreme effects resulting from the combination of these parameters. We stress that our focus is on qualitative rather than quantitative agreement with the data, and thus we do not attempt to find the optimal set of parameters through methods such as MCMC.

Figure \ref{fig:ofe-feh-best} presents the stellar [O/Fe]--[Fe/H]--age distributions as a function of $R_{\rm gal}$ and $|z|$ predicted by the best multi-zone model.
